A GRASP algorithm for the concrete delivery problem.

### 2023-08-09 Article/article.tex
Save article

\section{Computational results}
\label{comp_exp}

In this section, we present and discuss the results of the computational experiments of the GRASP heuristic described in section~\ref{grasp_method}. The GRASP algorithm is coded in C++. We run our experiments on a dataset extracted from data provided by our industrial partner.

\subsection{Generation of instances}

The dataset used in this section was obtained from our partner and contains records representing delivery operations from up to 8 production centers over a period of 50 days. We generated 50 instances, with each instance corresponding to a daily operation. The instances include informations such as each driver capacity, associated depot, and shift start time. For each customer, we have the due time, total demand, and the number of orders (type of concrete) received. For each order, we specified its demand and associated production plant. Finally, we include loading capacities for each production center. 
The name of an instance has the format $C\_k\_n\_o\_z$. $k$ is the number of available drivers, $n$ the number of customers, $o$ the total number of daily orders, and $z$ the number of plants.

The dataset is subdivised in a small, medium and large sets, according to the number of drivers and total demands served. We summarized both sets in Table~\ref*{}
or 
The dataset is subdivised in a small, medium and large sets, according to the number of orders served. We summarized both sets in Table~\ref*{}

% This dataset allows us to evaluate the effectiveness and performance of our GRASP algorithm in optimizing delivery operations in a real-world setting.

\begin{itemize}
    \item   8 production centers located in greater Montreal
    \item   42 days of delivery operations from Fall 2020
    \item   From 7 to 139 orders each day
    \item   Up to 137 drivers
    \item   2 types of trucks of capacity 8 and 12 m$^3$
\end{itemize}

@@

\begin{tabular}{lrrrrrrr}
    \toprule
    {} &  satisfiedCost &  driverUsed &  travelCost &  firstDeliveryCost &  underWorkCost &  overTimeCost &  runtime \\
    Name     &                &             &             &                    &                &               &          \\
    \midrule
    20201121 &          226.5 &          13 &     1243.55 &               0.51 &           0.00 &          0.00 &     5.26 \\
    20201010 &          267.0 &          13 &      745.10 &               0.00 &           0.00 &          0.00 &     5.32 \\
    20201107 &          333.5 &          18 &      777.25 &               0.00 &         200.16 &          0.00 &     5.19 \\
    20201031 &          375.0 &          15 &     1017.64 &               0.00 &         216.06 &         28.10 &     5.42 \\
    20201114 &          388.0 &          19 &     1743.64 &               0.00 &         149.48 &          0.00 &     5.42 \\
    20201128 &          776.0 &          31 &     2278.18 &               0.00 &           4.19 &        438.14 &     5.16 \\
    20201024 &          937.5 &          35 &     4403.57 &               0.00 &          58.30 &       1005.24 &     5.72 \\
    20201021 &         1160.5 &          73 &     6107.22 &               0.00 &        2535.40 &        185.02 &     5.28 \\
    20201013 &         1565.0 &         102 &     9214.74 &              19.53 &        2955.35 &         95.74 &     5.32 \\
    20201026 &         1839.5 &         116 &    13585.60 &              44.44 &        1826.70 &        227.56 &     5.41 \\
    20201007 &         2512.5 &         127 &    15166.00 &               5.09 &         877.68 &        574.76 &     5.67 \\
    \bottomrule
    \end{tabular}
    }
\end{table}

>>>>

\section{Computational experiments}
\label{comp_exp}

In this section, we present and discuss the results of the computational experiments of the GRASP heuristic described in section~\ref{grasp_method}. The GRASP algorithm is coded in C++. We run our experiments on a dataset extracted from delivery operations records provided by our industry partner and on the benchmark data used in \cite{kinable2014concrete}.

\subsection{Generation of instances}
\newcommand{\nbInstance}{36}
The dataset used in this section was obtained from our partner and contains records representing delivery operations from up to 8 production centers over a period of $\nbInstance$ days. We have created $\nbInstance$ instances, where each instance corresponds to a daily operation. An instance contains information such as each driver's capacity, associated batch plant, and shift start time. For each customer, we have the due time, the total demand, and the number of orders (type of concrete) received. For each order, we have its demand and associated production plant. Finally, we have the loading capacity for each plant. The name of an instance has the format $C\_k\_n\_o\_z$, where $k$ is the number of available drivers, $n$ is the number of customers, $o$ is the total number of daily orders, and $z$ is the number of plants. The dataset is divided into small, medium, and large sets according to the total number of daily orders. We have summarized the data set in the table~\ref{tab:instances}.

\begin{table}[htpb]
    \caption{Instances summary}
    \label{tab:instances}
    \resizebox*{\textwidth}{!}{
    \begin{tabular}{lcccccc}
        \toprule
        {} &  \# &           Load  &   \#Order & \#Client &  \#Driver & \#Depot \\
          &       &         (m$^3$)        &         &         &          &        \\
        \midrule
        Small  &     8 &    226.5-957.5 &     7-15 &    4-11 &    13-39 &    1-3 \\
        Medium &    14 &  1,164.5-2,971.0 &    44-98 &   41-89 &   76-140 &    6-8 \\
        Large  &    14 &  3,078.5-3,953.5 &  107-137 &  92-128 &  133-153 &    8-8 \\
        \bottomrule
        \end{tabular}  
    }
\end{table}

@@

    \begin{tabular}{llrrrrrrrr}
        \toprule
              &                 &  satisfiedCost &  travelCost &  firstDeliveryCost &  maxfirstDelivery &  underWorkCost &  overTimeCost &  driverUsed &  runtime \\
        size & Instance &                &             &                    &                   &                &               &             &          \\
        \midrule
        small & C\_15\_4\_7\_2 &          375.0 &     1013.11 &               0.00 &              0.00 &          56.79 &        244.61 &          15 &  3009.54 \\
              & C\_19\_7\_8\_2 &          388.0 &     1714.74 &               0.00 &              0.00 &          97.56 &        283.83 &          19 &  3020.89 \\
              & C\_13\_5\_8\_1 &          267.0 &      745.10 &               0.00 &              0.00 &           0.00 &          0.00 &          13 &  3027.39 \\
              & C\_31\_8\_11\_3 &          776.0 &     2297.20 &               0.00 &              0.00 &         627.37 &        539.96 &          30 &  3033.85 \\
              & C\_39\_10\_11\_3 &          937.5 &     4077.20 &               0.00 &              0.00 &         720.00 &        866.98 &          31 &  3020.75 \\
              & C\_18\_6\_11\_2 &          333.5 &      753.26 &               0.00 &              0.00 &         653.78 &          0.00 &          17 &  3004.51 \\
              & C\_13\_11\_12\_1 &          226.5 &     1243.55 &               0.00 &              0.00 &          66.01 &          0.00 &          13 &  3022.06 \\
              & C\_35\_11\_15\_3 &          613.5 &     3724.29 &              12.41 &             12.41 &         246.04 &        454.51 &          28 &  3035.23 \\
        Medium & C\_76\_41\_44\_6 &         1160.5 &     5715.53 &               1.00 &              1.00 &        3566.49 &        771.23 &          69 &  3021.92 \\
              & C\_104\_42\_47\_8 &         1565.0 &     9114.62 &              23.00 &             16.24 &        4180.95 &        671.94 &          94 &  3047.99 \\
              & C\_98\_63\_70\_7 &         1746.5 &    13888.90 &              19.86 &             12.40 &        1086.60 &       1477.76 &          94 &  3025.72 \\
              & C\_118\_57\_70\_6 &         2327.5 &    15066.80 &              83.79 &             16.44 &        1522.11 &       1892.64 &         117 &  3020.70 \\
              & C\_130\_68\_74\_7 &         2595.0 &    19133.50 &             251.77 &             54.40 &        1523.19 &       2924.28 &         128 &  3053.96 \\
              & C\_117\_67\_78\_8 &         1839.5 &    13946.30 &              44.68 &              9.98 &        1578.90 &        639.28 &         116 &  3007.88 \\
              & C\_128\_66\_80\_8 &         2512.5 &    15177.80 &               2.00 &              2.00 &        1874.83 &        965.65 &         125 &  3007.70 \\
              & C\_120\_71\_82\_8 &         2060.0 &    12461.20 &              68.38 &             20.06 &        3119.66 &       1478.63 &         107 &  3028.24 \\
              & C\_140\_79\_83\_7 &         2425.0 &    18811.40 &             252.94 &             41.65 &        2193.63 &       1963.05 &         136 &  3025.83 \\
              & C\_129\_78\_85\_8 &         2685.5 &    16927.30 &             202.26 &             50.12 &        1492.50 &       2794.21 &         128 &  3030.32 \\
              & C\_133\_80\_89\_8 &         2893.5 &    17572.10 &             187.42 &             49.24 &        1803.22 &       1306.94 &         130 &  3040.74 \\
              & C\_136\_85\_97\_8 &         2673.0 &    16832.10 &             154.97 &             50.21 &        3507.40 &       1958.58 &         132 &  3028.15 \\
              & C\_137\_89\_97\_7 &         2939.5 &    21934.10 &             697.18 &             59.10 &        1220.15 &       3038.33 &         137 &  3025.45 \\
              & C\_135\_84\_98\_7 &         2971.0 &    22399.30 &             867.12 &             59.44 &         550.77 &       2887.51 &         133 &  3137.11 \\
        Large & C\_143\_92\_107\_8 &         3684.5 &    22700.20 &             147.42 &             48.31 &         899.82 &       3702.01 &         142 &  3019.52 \\
              & C\_141\_98\_108\_8 &         3541.0 &    20550.10 &             566.69 &             57.49 &        1438.11 &       2910.97 &         139 &  3011.84 \\
              & C\_133\_98\_109\_8 &         3078.5 &    23102.40 &             193.01 &             49.44 &         450.57 &       3931.83 &         132 &  3018.05 \\
              & C\_133\_101\_119\_8 &         3229.0 &    18978.90 &             467.94 &             59.47 &        1084.78 &       2334.16 &         129 &  3179.81 \\
              & C\_145\_108\_122\_8 &         3670.5 &    23401.60 &             668.15 &             59.77 &        1438.60 &       3569.62 &         143 &  3056.51 \\
              & C\_144\_101\_123\_8 &         3437.5 &    24560.70 &             451.36 &             56.61 &        1663.43 &       4359.64 &         142 &  3039.02 \\
              & C\_153\_99\_123\_8 &         3513.0 &    20696.60 &             839.56 &             52.60 &        2465.87 &       2892.55 &         149 &  3072.58 \\
              & C\_146\_114\_129\_8 &         3499.5 &    21991.50 &             898.10 &             55.22 &        1750.60 &       4943.03 &         142 &  3011.54 \\
              & C\_142\_112\_129\_8 &         3471.0 &    21526.10 &             252.62 &             58.09 &         624.87 &       3360.64 &         137 &  3018.76 \\
              & C\_153\_112\_131\_8 &         3953.5 &    25455.30 &             868.81 &             49.15 &         500.68 &       3775.57 &         148 &  3005.96 \\
              & C\_144\_114\_132\_8 &         3401.5 &    23259.00 &            1092.82 &             57.99 &         634.53 &       2705.26 &         140 &  3046.75 \\
              & C\_143\_114\_136\_8 &         3350.5 &    21760.00 &            1131.39 &             59.58 &        1284.13 &       2360.19 &         141 &  3056.56 \\
              & C\_153\_128\_137\_8 &         3946.5 &    25822.20 &             742.75 &             57.10 &         899.92 &       5101.58 &         150 &  3060.79 \\
              & C\_141\_115\_137\_8 &         3739.5 &    24670.70 &             750.04 &             55.88 &         518.63 &       5156.41 &         137 &  3021.26 \\
        \bottomrule
        \end{tabular}

    }
\end{table}
